Delocalization of Eigenvectors in Random Matrices

### 2025-03-20 Draft.tex
diffusion profile fix

\begin{equation}
\Rightarrow d{T} = {T}^2 dt + S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt
\end{equation}
Now, define $\Theta(t)=\Theta_t$ and $\epsilon_t(z)$ as:$$\Theta(t) = \frac{|m(z)|^2}{1-t|m(z)|^2S}\Leftrightarrow d\Theta_t = \Theta_t^2 dt$$
$$\E_t(z):T_t(z)-\Theta_t$$
$$\Rightarrow d\E_t(z) = T_t(z)^2dt + \Theta_t^2dt-S^{1/2}dM_t(z)S^{1/2}+S^{1/2}\Omega_t(z)S^{1/2}dt=$$
 $$=\{\Theta_t \E_t(z)+\E_t(z)\Theta_t\}dt +\E_t^2(z)dt - S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt$$
by observing that $T_t(z)^2-\Theta_t^2=\Theta_t\E_t(z)+\E_t(z)\Theta_t+\E_t(z)^2$. Integrating $\E_t(z)$ over $s$:
$$\E_t(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\left\{\E^2(s)ds +S^{1/2} dM(s)S^{1/2}+  S^{1/2} \Omega(s) S^{1/2}\right\} \{\text{Id} + (t-s)\Theta_t\}ds,$$
whereas we can split the terms in three separate components, each of which we will individually bound in the following section:

@@

\subsection{Stopping time}

>>>>

\begin{equation}
\Rightarrow d{T} = {T}^2 dt + S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt
\end{equation}
Now, define the \textit{time-dependent diffusion profile} as:$$\Theta_t = \frac{|m(z)|^2S}{1-t|m(z)|^2S}$$
Let us take its derivative w.r.t to $t$: 
$$\frac{d\Theta_t}{dt} = \frac{d}{dt}\frac{|m(z)|^2S}{1-t|m(z)|^2S} = \frac{-|m(z)|^2S(-|m(z)|^2S)}{(1-t|m(z)|^2S)^2} = \Theta_t^2 \Leftrightarrow d\Theta_t = \Theta_t^2 dt$$

$$\partial_{t}\{\text{Id}+(t-s)\Theta_t\} = \Theta_t+(t-s)\Theta_t^2=\Theta_t\frac{1-t|m(z)|^2S+(t-s)|m(z)|^2S}{1-t|m(z)|^2S}=$$
$$=\Theta_t \frac{1-s|m(z)|^2S}{1-t|m(z)|^2S}=\Theta_t\{\text{Id}+(t-s)\Theta_t\}$$
Let $\mathcal{E}_t(z)$ be the fluctuation term, i.e the difference between our $T$-matrix and the diffusion profile:
$$\E_t(z):T_t(z)-\Theta_t$$
Let us compute its evolution equation: 
$$\Rightarrow d\E_t(z) = T_t(z)^2dt + \Theta_t^2dt-S^{1/2}dM_t(z)S^{1/2}+S^{1/2}\Omega_t(z)S^{1/2}dt=$$
 $$=\{\Theta_t \E_t(z)+\E_t(z)\Theta_t\}dt +\E_t^2(z)dt - S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt$$
by observing that $T_t(z)^2-\Theta_t^2=\Theta_t\E_t(z)+\E_t(z)\Theta_t+\E_t(z)^2$. Integrating $\E_t(z)$ over $s$:
$$\E_t(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\left\{\E^2(s)ds +S^{1/2} dM(s)S^{1/2}+  S^{1/2} \Omega(s) S^{1/2}\right\} \{\text{Id} + (t-s)\Theta_t\}ds,$$
whereas we can split the terms in three separate components, each of which we will individually bound in the following section:

@@

\subsection{Stopping time}
If we examine the three terms in the last section, we can see that
